\section{introduction}
The expected redshift $z(r)$ is a combination of the gravitational redshift $z_g(r)$ and the full relativistic Doppler shift $z_D$ \citep{2006ApJ...639L..21Z}, \begin{equation}
	\label{eqn:redshift}
	z(r) = z_g(r) + z_D(r)
\end{equation}

\subsubsection*{Gravitational redshift}
The gravitational redshift is given by \begin{equation}
	\label{eqn:gravitational-redshift}
	z_g(r) = \frac{g_{00}(R)}{g_{00}(r)} - 1
\end{equation} where $r$ is the position of the emitted photon (emitter or source) and $R$ is the position of the receiver. Here, $R = R_\odot \approx \SI{8}{\kilo\parsec}$ is the distance of the sun to the galactic center. For a spherically symmetric metric with $g_{00}(r) = \e^{\nu(r)}$ \cref{eqn:gravitational-redshift} becomes \begin{equation}
	z_g(r) = \e^{[\nu(R) - \nu(r)]/2} - 1
\end{equation} In the special case of a BH the $00$-component of the metric is given by $g_{00}(r) = (1 - r_{\rm Sch}/r)$ with the Schwarzschild radius $r_{\rm Sch} = 2 G M/c^2$, the BH mass $M$, the gravitational constant $G$ and the speed of light $c$. For an emitter close to the galactic center we have $r/R_\odot \ll 1$. The gravitational redshift simplifies then to \begin{equation}
	\label{eqn:gravitational-redshift:BH:approx}
	z_g(r) \approx \frac12 \frac{r_{\rm Sch}}{r}
\end{equation} Further, it is assumed that the emitter is not to close to the central compact object such that its orbit is Keplerian to a good approximation. Following the vis-viva equation yields \begin{equation}
	\label{eqn:vis-viva}
	\beta(r)^2 \approx \frac{r_{\rm Sch}}{r} - \frac{r_{\rm Sch}}{2 a}
\end{equation} with the semi-major axis $a$. Finally, \cref{eqn:gravitational-redshift:BH:approx,eqn:vis-viva} give \begin{equation}
	z_g(r) \approx \frac{r_{\rm Sch}}{4a} + \frac12 \beta(r)^2
\end{equation} with the substitution $\beta(r) = v(r)/c$ and $v(r)$ the object's velocity.

\subsubsection*{Full relativistic Doppler shift}
The full relativistic Doppler shift is given by \begin{equation}
	\label{eqn:Doppler-shift}
	z_D(r) = \frac{1 + \beta(r) \cos\vartheta}{\sqrt{1 - \beta(r)^2}} - 1
\end{equation} where $\vartheta$ is the angle between the velocity vector and the line of sight. Of interest here is only the transverse Doppler shift, given for $\theta=\pi/2$, what is a prediction of Special Relativity. For small velocities $\beta(r) \ll 1$ the transverse Doppler shift $z_{tD}(r)$ becomes \begin{equation}
	z_{tD} \approx \frac12 \beta(r)^2
\end{equation}


\subsubsection*{Redshift comparison at the S2 pericenter}
In the following, the combined gravitational redshift and relativistic transverse Doppler effect at the pericenter of the S2 star will be compared with the RAR prediction.

The former redshift based on the S2 orbit parameters is calculated via \begin{equation}
	\label{eqn:redshift:Kepler}
	z(r_p) \approx \frac{r_{\rm Sch}}{4a} + \beta(r_p)^2
\end{equation} where the velocity at the pericenter is given by \begin{equation}
	v_p^2 = \frac{G M}{a} \frac{1 + e}{1 - e}
\end{equation} The numerical values of the orbit parameters (e.g. $M$, $a$ and $e$) are provided in \citet[][Table A.1]{2018A&A...615L..15G}. Note that the semi-major axis $a$ is given there only in $mas$. It is therefore convenient to calculate its value via \begin{equation}
	a^3 = \frac{G M T^2}{4 \pi^2}
\end{equation} where $T$ is the orbit period. The relative uncertainty of \cref{eqn:redshift:Kepler} is given by \begin{equation}
	\Delta z(r_p) = \frac{\Delta M}{M} + \frac{\Delta a}{a} + \frac{4 \Delta e}{(1 - e)(3 + e)} \approx \SI{1.1}{\percent}
\end{equation} while the uncertainty of the pericenter is given by \begin{equation}
	\Delta r_p = \frac{\Delta a}{a} + \frac{\Delta e}{1 - e} \approx \SI{0.3}{\percent}
\end{equation}

In the RAR case the redshift is calculated by \cref{eqn:redshift,eqn:gravitational-redshift,eqn:Doppler-shift} with $\vartheta = \pi/2$ in order to take into account only the transverse Doppler shift. In sum \begin{equation}
	\label{eqn:redshift:RAR}
	z(r_p) = \frac{1}{\sqrt{1 - \beta(r_p)^2}} + \e^{[\nu(R) - \nu(r_p)]/2} - 2
\end{equation}

It is important to emphasize that the calculated redshifts, given by \cref{eqn:redshift:Kepler,eqn:redshift:RAR}, consider only the relativistic corrections. Thus, a deviation of the angle $\theta=\pi/2$ would contribute the Newtonian Doppler shift to both redshifts in the same amount. Additionally, it is expected that the Roemer time delay would contribute in the same way.\footnote{To me it is not completely clear yet how to include the effect due to the Roemer time delay. And if it is necessary at all.}